Comparing and contrasting with prior work in the field

### 2014-03-04 response/response.tex

 \item Pg. 1: In line 46, replace “numeric differentiation” by “numerical differentiation”.

{\color{red}  
\begin{itemize}
     \item
      Manuscript corrected.
  \end{itemize}}

 \item Pg. 2: In line 25, the sentence “The distinction of “accurate” is deﬁned by ...”
awkward. Please revise it.

{\color{red}  
\begin{itemize}
     \item
      Manuscript corrected. It is made clear that CS is being compared with FD, CD where AD is the standard used for the comparison.
  \end{itemize}}

@@

 \item Pg. 4: In lines 45-46, “(add, multiply, power, transcendental and the like)” should
probably be “(addition, multiplication, exponentiation, and the like)” or similar.

{\color{red}  
\begin{itemize}
     \item
 Manuscript corrected. 
  \end{itemize}}

 \item Pg. 4: In line 47, I would replace “used in the study” by “used in this study”. Similarly,
in other instances of the manuscript.

 \item Pg. 5: In line 39, you may replace “the partials” by “the partial derivatives”. Similarly
in page 26.

@@

 \item Pg. 5: I would replace the title of Section 1.2 “Tangent-stiffness” by “Tangent-stiffness
matrix”. Similarly, in line 50.

{\color{red}  
\begin{itemize}
     \item
 Manuscript corrected. 
  \end{itemize}}

 \item Pg. 6: In line 14, “quasi-Newton’s method’s” should probably be “quasi-Newton
methods”.

 \item Pg. 6: In line 18, “about about a particular” should be “about a particular”.
